%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------


\documentclass[10pt]{sigplanconf}

% The following \documentclass options may be useful:

% preprint      Remove this option only once the paper is in final form.
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{listings,lstcoq,lsterlang}
\usepackage{bcprules}
%\usepackage{url}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{enumitem}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}


\lstdefinestyle{default}{
  language=coq,
  basicstyle={\ttfamily\normalsize},
  breaklines=true,
  % frame=tb,
  framesep=6pt,
  captionpos=b,
  numberstyle=\scriptsize,
  numbers=left,
  numbersep=6pt,
  xleftmargin=12pt,
  aboveskip=1em,
  belowskip=1em,
}
\lstdefinestyle{small}{
  style=default,
  basicstyle={\ttfamily\small},
}
\lstset{
  style=default
}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{AGERE!@SPLASH}{Oct., 2015, Pittsburgh, PA, USA}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
\doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the
% traditional copyright transfer agreement.

%\exclusivelicense                % ACM gets exclusive license to publish,
                                  % you retain copyright

%\permissiontopublish             % ACM gets nonexclusive license to publish
                                  % (paid open-access papers,
                                  % short abstracts)

%% \titlebanner{banner above paper title}        % These are ignored unless
%% \preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Actario: A Framework for Reasoning About Actor Systems}
%% \subtitle{Subtitle Text, if any}

\authorinfo{Shohei Yasutake}
           {Tokyo Institute of Technology}
           {yasutake@psg.cs.titech.ac.jp}
\authorinfo{Takuo Watanabe}
           {Tokyo Institute of Technology}
           {takuo@acm.org}

\maketitle

\begin{abstract}
The two main characteristics of the Actor model are asynchronous message passing and dynamic system topology. The latter relies on the on-the-fly creation of actor names that often complicates the formal treatment of systems described in the Actor model. In this paper, we introduce Actario, a formalization of the Actor model in Coq. Actario incorporates a name creation mechanism that is formally proved to generate a consistent set of actor names. The mechanism helps proper handling of names in modeling and reasoning about actor-based systems. Actario also provides a code extraction mechanism that generates Erlang programs.
\end{abstract}

\category{F.3.2}{Logics and Meanings of Programs}%
{Specifying and Verifying and Reasoning about Programs}%
[Mechanical verification]

% general terms are not compulsory anymore,
% you may leave them out
\terms{Actors, Formal Models}

\keywords{Actor Model, Formalization, Actario, Coq, Erlang}

\input{./introduction.tex}
\input{./overview.tex}
\input{./semantics.tex}
\input{./uniqueness.tex}
\input{./fairness.tex}
\input{./extraction.tex}
\input{./related-work.tex}
\input{./conclusion.tex}
\input{./appendix.tex}

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{15}
\softraggedright
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Actario()]{Actario}
Actario.
\newblock Actario: A framework for verifying actor based systems.
\newblock \url{https://github.com/amutake/actario}.

\bibitem[Affeldt and Kobayashi(2008)]{Affeldt200817}
R.~Affeldt and N.~Kobayashi.
\newblock A {Coq} library for verification of concurrent programs.
\newblock In \emph{Fourth International Workshop on Logical Frameworks and
  Meta-Languages (LFM 2004)}, volume 199 of \emph{Electronic Notes in
  Theoretical Computer Science}, pages 17--32, 2008.
\newblock \doi{10.1016/j.entcs.2007.11.010}.
\newblock URL
  \url{http://www.sciencedirect.com/science/article/pii/S1571066108000765}.

\bibitem[Agha(1986)]{Agha:1986aa}
G.~Agha.
\newblock \emph{Actors: A Model of Concurrent Computation in Distributed
  Systems}.
\newblock MIT Press, 1986.
\newblock URL \url{http://mitpress.mit.edu/books/actors}.

\bibitem[Akka()]{Akka}
Akka.
\newblock Akka.
\newblock \url{http://akka.io/}.

\bibitem[Arkoudas()]{Athena}
K.~Arkoudas.
\newblock Athena.
\newblock \url{http://proofcentral.org/athena}.

\bibitem[{De Koster} et~al.(2012){De Koster}, {Van Cutsem}, and
  D'Hondt]{De-Koster:2012aa}
J.~{De Koster}, T.~{Van Cutsem}, and T.~D'Hondt.
\newblock Domains: Safe sharing among actors.
\newblock In \emph{Proceedings of the 2nd edition on Programming Systems,
  Languages and Applications based on Actors, Agents, and Decentralized Control
  Abstractions (AGERE!@SPLASH 2012)}, pages 11--22. ACM, ACM, 2012.
\newblock \doi{10.1145/2414639.2414644}.

\bibitem[Erlang()]{Erlang}
Erlang.
\newblock Erlang programming language.
\newblock \url{http://www.erlang.org/}.

\bibitem[Garnock-Jones et~al.(2014)Garnock-Jones, Tobin-Hochstadt, and
  Felleisen]{Garnock-Jones:2014aa}
T.~Garnock-Jones, S.~Tobin-Hochstadt, and M.~Felleisen.
\newblock The network as a language construct.
\newblock In \emph{Programming Languages and Systems (ESOP 2014)}, volume 8410
  of \emph{Lecture Notes in Computer Science}, pages 473--492. Springer-Verlag,
  2014.
\newblock \doi{10.1007/978-3-642-54833-8_25}.
\newblock URL \url{http://www.ccs.neu.edu/home/tonyg/esop2014/}.

\bibitem[Musser and Varela(2013)]{Musser:2013aa}
D.~R. Musser and C.~A. Varela.
\newblock Structured reasoning about actor systems.
\newblock In \emph{Workshop on Programming based on Actors, Agents, and
  Decentralized Control (AGERE!@SPLASH 2013)}, pages 37--48. ACM, oct 2013.
\newblock \doi{10.1145/2541329.2541334}.

\bibitem[Scala()]{Scala}
Scala.
\newblock The {Scala} programming language.
\newblock \url{http://scala-lang.org/}.

\bibitem[Sirjani and Jaghoori(2011)]{Sirjani:2011aa}
M.~Sirjani and M.~M. Jaghoori.
\newblock Ten years of analyzing actors: {Rebeca} experience.
\newblock In G.~Agha, O.~Danvy, and J.~Meseguer, editors, \emph{Formal
  Modeling: Actors, Open Systems, Biological Systems}, volume 7000 of
  \emph{Lecture Notes in Computer Science}, pages 20--56. Springer-Verlag,
  2011.
\newblock \doi{10.1007/978-3-642-24933-4_3}.

\bibitem[Talcott et~al.(2011)Talcott, Sirjani, and Ren]{Talcott:2011aa}
C.~Talcott, M.~Sirjani, and S.~Ren.
\newblock Comparing three coordination models: {Reo}, {ARC}, and {PBRD}.
\newblock \emph{Science of Computer Programming}, 76\penalty0 (1):\penalty0
  3--22, 2011.
\newblock \doi{10.1016/j.scico.2009.11.006}.

\bibitem[Watanabe(2013)]{Watanabe:2013aa}
T.~Watanabe.
\newblock Towards a compositional reflective architecture for actor-based
  systems.
\newblock In \emph{Workshop on Programming based on Actors, Agents, and
  Decentralized Control (AGERE!@SPLASH 2013)}, pages 19--24. ACM, oct 2013.
\newblock \doi{10.1145/2541329.2541341}.

\bibitem[Wilcox et~al.(2015)Wilcox, Woos, Panchekha, Tatlock, Wang, Ernst, and
  Anderson]{Verdi}
J.~R. Wilcox, D.~Woos, P.~Panchekha, Z.~Tatlock, X.~Wang, M.~D. Ernst, and
  T.~Anderson.
\newblock Verdi: A framework for implementing and formally verifying
  distributed systems.
\newblock In \emph{Proceedings of the 36th ACM SIGPLAN Conference on
  Programming Language Design and Implementation}, PLDI 2015, pages 357--368,
  New York, NY, USA, 2015. ACM.
\newblock ISBN 978-1-4503-3468-6.
\newblock \doi{10.1145/2737924.2737958}.
\newblock URL \url{http://doi.acm.org/10.1145/2737924.2737958}.

\bibitem[Yonezawa et~al.(1986)Yonezawa, Briot, and Shibayama]{Yonezawa:1986aa}
A.~Yonezawa, J.-P. Briot, and E.~Shibayama.
\newblock Object-oriented concurrent programming in {ABCL/1}.
\newblock In \emph{OOPSLA '86 Conference Proceedings on Object-Oriented
  Programming Systems, Languages and Applications}, pages 258--268, 1986.
\newblock \doi{10.1145/960112.28722}.

\end{thebibliography}


\end{document}

%                       Revision History
%                       -------- -------
%  Date         Person  Ver.    Change
%  ----         ------  ----    ------

%  2013.06.29   TU      0.1--4  comments on permission/copyright notices
